\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Omar Ahmad Al Blooshi} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+971 52 822 2985 \\ Dubai, UAE} 
\address{\href{mailto:omarahmadp91@gmail.com}{omarahmadp91@gmail.com} \\ \href{https://github.com/omardevelops}{github.com/omardevelops}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE (SUMMARY) - PAGE 1
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Software Engineer and Khalifa University graduate with 4+ years of industry experience, specializing in full-stack web development, cloud architecture (AWS), and data engineering. Seeking roles to build impactful and innovative solutions.}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE - PAGE 1
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}

\textbf{Associate Solutions Architect} \hfill May 2024 -- Present\\
Amazon Web Services (AWS) EMEA \hfill \textit{Dubai, UAE}
 \begin{itemize}
    \itemsep -3pt {}
     \item Designed and built a serverless class scheduling system using Lambda, API Gateway, and Amplify in 3 weeks.
     \item Developed a ``single pane of glass'' POC for organizational data using Amazon SageMaker Unified Studio to support analytics, AI/ML, and GenAI projects.
     \item Designed secure, scalable AWS architectures driving customer growth across MENAT.
     \item Earned AWS Certified Solutions Architect -- Associate and AWS Cloud Practitioner certifications via a 5-month Tech U Program.
     \item Represented AWS at Ajman University, guiding students on Amazon career paths.
 \end{itemize}

\textbf{Full Stack Engineer} \hfill Aug 2025 -- Mar 2026\\
DroneLeaf (Khalifa University Spin-off) \hfill \textit{Abu Dhabi, UAE}
 \begin{itemize}
    \itemsep -3pt {}
     \item Participated in this project as part of Al Nokhba Program at Khalifa University.
     \item Built the frontend for the DroneLeaf Portal SaaS product (\href{https://droneleaf.io}{droneleaf.io}) from scratch in $\sim$6 months using Angular and TypeScript, meeting deadlines for internal beta and public release at UMEX 2026.
     \item Integrated frontend with an AWS backend and implemented web-to-IoT-device communication using MQTT.
     \item Delivered one of DroneLeaf's main product offerings to customers in the drone industry.
 \end{itemize}

\textbf{Data Engineer} \hfill Oct 2022 -- Apr 2024\\
Statistics Centre -- Abu Dhabi \hfill \textit{Abu Dhabi, UAE}
 \begin{itemize}
    \itemsep -3pt {}
     \item Engineered ETL pipelines using Informatica and Python, processing 2.5M+ daily records for BI and analytics.
     \item Contributed to data ingestion for the Abu Dhabi Census 2023 project.
     \item Developed internal documentation using Confluence, reducing team onboarding time by 50\%.
     \item Co-managed an unstructured data extraction initiative, driving budget savings through automation.
     \item Proficiently used SQL and resolved urgent data support requests from business users for SCAD website.
 \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS - PAGE 1
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\\\hspace{6ex}} l }
Front-End Development & HTML, CSS, JavaScript, TypeScript, React, Angular \\
Cloud \& Backend & AWS (Lambda, API Gateway, Amplify, SageMaker), MQTT \\
Data Engineering & Informatica Cloud Services, Python, SQL, ETL Pipelines \\
Other & iOS (Swift, Xcode), Docker, Java, Linux, Git \\
Soft Skills & Arabic \& English (Fluent), Public Speaking, Leadership, Teamwork \\
\end{tabular}\\
\end{rSection}

\newpage % Force second page for the remaining sections

%----------------------------------------------------------------------------------------
%	EDUCATION - PAGE 2
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf BSc Computer Engineering}, Khalifa University \hfill {2017 -- 2022}\\
GPA: 3.87 / 4.0

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS - PAGE 2
%----------------------------------------------------------------------------------------
\begin{rSection}{SIDE PROJECTS}
\vspace{-1.25em}
\item \textbf{Meeting \& Presentation Scheduling System.} {Senior Design Project at Khalifa University. A full system for scheduling meetings and presentations with automated management features.}
\item \textbf{Medicine Tracker App.} {iOS application built using Xcode and Swift for tracking medication schedules and reminders.}
\item \textbf{Hotel Booking System.} {Full-stack web application using MySQL, HTML, CSS, and PHP with a complete booking and management workflow.}
\item \textbf{Weather Forecast App.} {Web app that fetches and displays real-time weather data based on the user's search term via a weather API.}
\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS - PAGE 2
%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications}
\begin{itemize}
    \item AWS Certified Developer -- Associate
    \item AWS Certified Solutions Architect -- Associate
    \item AWS Certified Cloud Practitioner
    \item Arab Coders Full Stack Development Course -- Certificate of Completion
    \item freeCodeCamp HTML and CSS Course
    \item DP World Summer Internship 2021 -- Certificate of Completion
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	VOLUNTEERING - PAGE 2
%----------------------------------------------------------------------------------------
\begin{rSection}{Volunteering}
\begin{itemize}
    \item \textbf{Khalifa University} (2017--2022): Participated in the National Day play organized by the Emirati Club; helped organize and acted in the Japanese Club Scavenger Hunt event.
    \item \textbf{Applied Technology High School} (2016--2017): Walked in the White Cane Walk marathon at City Walk to raise awareness for the visually impaired; contributed Ramadan Mir box donation; served as receptionist at the Skills4Life event.
\end{itemize}
\end{rSection}

\vfill
\begin{center}
\textbf{References are available upon request.}
\end{center}



\end{document}
